Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-08-15 paper/document.tex
???

Several visualization tools have been created to understand how a software system changes over time. Wu \textit{et al.}~\cite{wu2004a} explored punctuated changes of software repositories with a tool that generates an Evolution Spectrograph. In this visualization, each file has a row in the chart and each cell represents a section of time where an incoming or outgoing dependency can be changed. The colour is determined by the frequency of change. This work was continued to show file directories and display the cardinality of a developer's commits in subsequent paper by Wu \textit{et al.}~\cite{wu2004}. The cardinality of a commit is the number of files or subsystems it affects in a system, indicating the scope of the change. Other tools also look at changes in code dependencies~\cite{6980224} or files~\cite{6650525, 7332421, voinea2006} over time. Alcocer \textit{et al.}~\cite{6650523} created a Performance Evolution Blueprint, which displays the changes in performance over time as a project evolves. Ogawa and Ma created code\_swarm~\cite{codeswarm}, a generative art visualization which presents the progressive evolution of file changes made by authors in a source control repository over time. Gource~\cite{gource} is a similar visualization, showing an animated force-directed tree of the file hierarchy as authors make changes to files in the source code repository over time. Ens \textit{et al.} created ChronoTwigger to visualize the co-evolution of source and test files~\cite{6980223}. This allowed testing practices to be more closely examined. Anslow \textit{et al.}~\cite{sourcevis} created SourceVis, a suite of software visualizations including visualizations for semantically-aware project evolution. SourceVis displays the evolution of Java source code metrics such as number of packages, classes, methods, and fields.

@@

A user study is needed to test the usefulness of TypeV. Some questions that need to be answered are: Can users new to a project easily find when major changes took place and, more importantly, what was being changed? Given a specific time period, can users find what was being worked on? The study should test TypeV against a line-based visualization such as GitHub’s graphs~\cite{github-graphs} and a file-based visualization such as code\_swarm~\cite{codeswarm}.

@@

A weakness of the timeline view described in this paper is that details about an author's activities are buried. As future work, the data extracted by TypeV can be used to create a visualization similar to Gource~\cite{gource} or code\_swarm~\cite{codeswarm}. These visualizations animate authors moving back-and-forth over files they edit; we proposed to animate authors' activities over \emph{types}. The focal point would be a particular type. The type itself may be represented abstractly as a shape or its UML representation that grows and shrinks as its usage increases and wanes over time.

>>>>

Several visualization tools have been created to understand how a software system changes over time. Wu \textit{et al.}~\cite{wu2004a} explored punctuated changes of software repositories with a tool that generates an Evolution Spectrograph. In this visualization, each file has a row in the chart and each cell represents a section of time where an incoming or outgoing dependency can be changed. The colour is determined by the frequency of change. This work was continued to show file directories and display the cardinality of a developer's commits in subsequent paper by Wu \textit{et al.}~\cite{wu2004}. The cardinality of a commit is the number of files or subsystems it affects in a system, indicating the scope of the change. Other tools also look at changes in code dependencies~\cite{6980224} or files~\cite{6650525, 7332421, voinea2006} over time. Alcocer \textit{et al.}~\cite{6650523} created a Performance Evolution Blueprint, which displays the changes in performance over time as a project evolves. Ogawa and Ma created \texttt{code\_swarm}~\cite{codeswarm}, a generative art visualization which presents the progressive evolution of file changes made by authors in a source control repository over time. Gource~\cite{gource} is a similar visualization, showing an animated force-directed tree of the file hierarchy as authors make changes to files in the source code repository over time. Ens \textit{et al.} created ChronoTwigger to visualize the co-evolution of source and test files~\cite{6980223}. This allowed testing practices to be more closely examined. Anslow \textit{et al.}~\cite{sourcevis} created SourceVis, a suite of software visualizations including visualizations for semantically-aware project evolution. SourceVis displays the evolution of Java source code metrics such as number of packages, classes, methods, and fields.

@@

A user study is needed to test the usefulness of TypeV. Some questions that need to be answered are: Can users new to a project easily find when major changes took place and, more importantly, what was being changed? Given a specific time period, can users find what was being worked on? The study should test TypeV against a line-based visualization such as GitHub’s graphs~\cite{github-graphs} and a file-based visualization such as \texttt{code\_swarm}~\cite{codeswarm}.

@@

A weakness of the timeline view described in this paper is that details about an author's activities are buried. As future work, the data extracted by TypeV can be used to create a visualization similar to Gource~\cite{gource} or \texttt{code\_swarm}~\cite{codeswarm}. These visualizations animate authors moving back-and-forth over files they edit; we proposed to animate authors' activities over \emph{types}. The focal point would be a particular type. The type itself may be represented abstractly as a shape or its UML representation that grows and shrinks as its usage increases and wanes over time.
